---
title: "Data visualisation in R"
author: "Malina Szychowska"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

I really enjoy visualizing data. I think that well chosen plot can tell more about the results than gianormous tables with rows and rows of number that make you dizzy. 
I like to plan the properties of the figures, so that they are easily understandable, self explanatory, accessible (e.g., for readers with colorblindness), and aesthetically pleasing. 

In this document you can find examples of different data visualisations I have prepared for different projects, and also visualizations of simulated data, just for the sake of showing off nice figures :) .

```{r import_datasets, message = FALSE, error = FALSE, warning = FALSE}

```

## Project 1. Sensory spatial memory {.tabset}

In this project I was comparing people performance on spatial memory game, when the task was to remember location of smells versus location of sounds. 

In short, participants first learned locations of smell and sound objects within a virtual reality arena that looked like a garden. Then they were asked to recall these locations at 3 occasions: 

1. Immediately after memorizing the locations in each condition.

2. After 15 minutes break.

3. After one week break.

First, I could look into individual data, and visualize: 

### Original and recalled locations 

```{r pressure}
plot(pressure)
```

### Walking paths from the start position to the recalled location

```{r pressure2}
plot(pressure)
```

